%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
%\bibitem{ref_article1}
%Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

%\bibitem{ref_lncs1}
%Author, F., Author, S.: Title of a proceedings paper. In: Editor, F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13. Springer, Heidelberg (2016). \doi{10.10007/1234567890}

%\bibitem{ref_book1}
%Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher, Location (1999)

%\bibitem{ref_proc1}
%Author, A.-B.: Contribution title. In: 9th International Proceedings on Proceedings, pp. 1--2. Publisher, Location (2010)

%\bibitem{ref_url1}
%LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4 Oct 2017

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%dedicated search:
%AKM97,BZL14,OMA95

%MILP search:
%MWG12,SHW14-1,SHW14-2,ZZDX19

%differential cryptanalysis:
%BS91,BS92

%linear cryptanalysis:
%M93,M94_1,M94_2

%ciphers
%Keccack:BDPV12,BDPVV14
%PRESENT:BKL07
%GIFT:BPP17
%Ascon:DEMS16
%AES:DR98,DR01,DR02
%RECTANGLE:ZBL15
%KNOT:ZDY19

%iterative trails
%K92,W08

%algorithms:
%J75,V03

%provable security
%R04
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibitem{AKM97}
Aoki, K., Kobayashi, K.,  Moriai, S. (1997, January). Best differential characteristic search of FEAL. In International Workshop on Fast Software Encryption (pp. 41-53). Springer, Berlin, Heidelberg.

\bibitem{BDPV12}
Bertoni, G., Daemen, J., Peeters, M.,  Van Assche, G. (2012). Permutation-based encryption, authentication and authenticated encryption. Directions in Authenticated Ciphers, 159-170.

\bibitem{BDPVV14}
Bertoni, G., Daemen, J., Peeters, M., Van Assche, G.,  Van Keer, R. (2014). CAESAR submission: Ketje v2. CAESAR First Round Submission, March.

\bibitem{BKL07}
Bogdanov, A., Knudsen, L. R., Leander, G., Paar, C., Poschmann, A., Robshaw, M. J., ...  Vikkelsoe, C. (2007, September). PRESENT: An ultra-lightweight block cipher. In International workshop on cryptographic hardware and embedded systems (pp. 450-466). Springer, Berlin, Heidelberg.

\bibitem{BPP17}
Banik S, Pandey SK, Peyrin T, Sasaki Y, Sim SM, Todo Y. GIFT: a small present. InInternational Conference on Cryptographic Hardware and Embedded Systems 2017 Sep 25 (pp. 321-345). Springer, Cham.

\bibitem{BS91}
Biham E, Shamir A. Differential cryptanalysis of DES-like cryptosystems. Journal of CRYPTOLOGY. 1991 Jan 1;4(1):3-72.

\bibitem{BS92}
Biham E, Shamir A. Differential cryptanalysis of the full 16-round DES. InAnnual International Cryptology Conference 1992 Aug 16 (pp. 487-496). Springer, Berlin, Heidelberg.

\bibitem{BZL14}
Bao Z, Zhang W, Lin D. Speeding up the search algorithm for the best differential and best linear trails. In International Conference on Information Security and Cryptology 2014 Dec 13 (pp. 259-285). Springer, Cham.

\bibitem{DEMS16}
Dobraunig C, Eichlseder M, Mendel F, Schläffer M. Ascon v1.2. Submission to the CAESAR Competition. 2016 Sep 15.

\bibitem{DR98}
Daemen J, Rijmen V. The block cipher Rijndael. InInternational Conference on Smart Card Research and Advanced Applications 1998 Sep 14 (pp. 277-284). Springer, Berlin, Heidelberg.

\bibitem{DR01}
Daemen J, Rijmen V. The wide trail design strategy[C]//IMA International Conference on Cryptography and Coding. Springer, Berlin, Heidelberg, 2001: 222-238.

\bibitem{DR02}
Daemen J, Rijmen V. The design of Rijndael[M]. New York: Springer-verlag, 2002.

\bibitem{J75}
Johnson DB. Finding all the elementary circuits of a directed graph. SIAM Journal on Computing. 1975 Mar;4(1):77-84.

\bibitem{K92}
Knudsen LR. Iterative Characteristics of DES and s 2-DES. InAnnual International Cryptology Conference 1992 Aug 16 (pp. 497-511). Springer, Berlin, Heidelberg.
\bibitem{M93}
Matsui M. Linear cryptanalysis method for DES cipher. InWorkshop on the Theory and Application of of Cryptographic Techniques 1993 May 23 (pp. 386-397). Springer, Berlin, Heidelberg.

\bibitem{M94_1}
Matsui M. The first experimental cryptanalysis of the Data Encryption Standard. InAnnual International Cryptology Conference 1994 Aug 21 (pp. 1-11). Springer, Berlin, Heidelberg.

\bibitem{M94_2}
Matsui M. On correlation between the order of S-boxes and the strength of DES. InWorkshop on the Theory and Application of of Cryptographic Techniques 1994 May 9 (pp. 366-375). Springer, Berlin, Heidelberg.

\bibitem{MWG12}
Mouha N, Wang Q, Gu D, Preneel B. Differential and linear cryptanalysis using mixed-integer linear programming. InInternational Conference on Information Security and Cryptology 2011 Nov 30 (pp. 57-76). Springer, Berlin, Heidelberg.

\bibitem{OMA95}
Ohta K, Moriai S, Aoki K. Improving the search algorithm for the best linear expression. InAnnual International Cryptology Conference 1995 Aug 27 (pp. 157-170). Springer, Berlin, Heidelberg.

\bibitem{R04}
Rogaway P. Nonce-based symmetric encryption. InInternational Workshop on Fast Software Encryption 2004 Feb 5 (pp. 348-358). Springer, Berlin, Heidelberg.

\bibitem{SHW14-1}
Sun S, Hu L, Wang P, Qiao K, Ma X, Song L. Automatic security evaluation and (related-key) differential characteristic search: application to SIMON, PRESENT, LBlock, DES (L) and other bit-oriented block ciphers. InInternational Conference on the Theory and Application of Cryptology and Information Security 2014 Dec 7 (pp. 158-178). Springer, Berlin, Heidelberg.

\bibitem{SHW14-2}
Sun S, Hu L, Wang M, Wang P, Qiao K, Ma X, Shi D, Song L, Fu K. Towards finding the best characteristics of some bit-oriented block ciphers and automatic enumeration of (related-key) differential and linear characteristics with predefined properties. IACRCryptology ePrint Archive. 2014;747:2014.

\bibitem{V03}
Vajnovszki V. A loopless algorithm for generating the permutations of a multiset. Theoretical Computer Science. 2003 Oct 7;307(2):415-31.

\bibitem{W08}
Wang M. Differential cryptanalysis of reduced-round PRESENT. InInternational Conference on Cryptology in Africa 2008 Jun 11 (pp. 40-49). Springer, Berlin, Heidelberg.

\bibitem{ZBL15}
Zhang W, Bao Z, Lin D, Rijmen V, Yang B, Verbauwhede I. RECTANGLE: a bit-slice lightweight block cipher suitable for multiple platforms. Science China Information Sciences. 2015 Dec 1;58(12):1-5.

\bibitem{ZDY19}
Wentao Zhang, Tianyou Ding, Bohan Yang, Zhenzhen Bao, Zejun Xiang, Fulei Ji, Xuefeng Zhao. KNOT: Algorithm Specifications and Supporting Document. \url{https://csrc.nist.gov/CSRC/media/Projects/lightweight-cryptography/documents/round-2/spec-doc-rnd2/knot-spec-round.pdf}

\bibitem{ZZDX19}
Zhou C, Zhang W, Ding T, Xiang Z. Improving the MILP-based Security Evaluation Algorithms against Differential Cryptanalysis Using Divide-and-Conquer Approach. IACR Cryptology ePrint Archive. 2019;2019:19.

%TODO: SAT search references

%TODO: generating graph references



\end{thebibliography}