\section{Preliminaries}\label{sec:pre}

A block cipher is a function $\calE:\bbF_2^k \times \bbF_2^n \rightarrow \bbF_2^n$ with $C=\calE(K,P)$ where $K$, $P$ and $C$ are the $k$-bit master key, $n$-bit plaintext and $n$-bit ciphertext. $k$ is the key size and $n$ is the block size. Embedded into an mode of operation, a block cipher can be used to encrypt a message with arbitrary length. 

A permutation is a function $\calP:\bbF_2^n \rightarrow \bbF_2^n$ with $SO=\calP(SI)$ where $SI$ and $SO$ are the $n$-bit input and output state. The sponge/duplex construction where a permutation is embedded can build various primitives such as a hash function, a stream cipher, a MAC or an authenticated encryption scheme \cite{bertoni2007sponge}. Note that a block cipher with key fixed $\calE_K=\calE(K,\cdot)$ can be seen as a permutation.

In this paper, we focus on symmetric-key primitives including iterated key-alternating SPN block ciphers and primitives based on SPN permutations. The state of such a primitive can be seperated into $m$ words of $s$ bits and it holds that $n=s\times m$. The round function of the $i$-th round consists of three layers and is denoted by $\calR_i=\calL\circ\calS\circ\calA_{W_i}$ where the three layers are:
\begin{itemize}
    \item Addition layer $\calA_{W_i}$: xor the $i$-th $n$-bit round key or constant $W_i$ to the state;
    \item Non-linear layer $\calS$: apply $m$ parallel $s$-bit S-boxes to the words, i.e.
    \begin{align*}
        \calS=\calS_0||\cdots||\calS_{m-1};
    \end{align*}
    \item Linear layer $\calL$: multiply an $n\times n$ bijective binary matrix to the state. 
\end{itemize}
\input{SPN.tex}
We use $W_i$ to denote the $i$-th round key for a block cipher or round constant for a permutation. The primitive iterates the round function $r$ times (See Fig. \ref{fig:SPN}). We denote the $i$-th round function excluding the addition layer by $\calR_i^*=\calL\circ\calS$. We denote the states before the non-linear layer, before the linear layer and after the linear layer of the $i$-th round function by $X_i$, $Y_i$ and $Z_i$. $X_i[j]$ denotes the $j$-th word of $X_i$, i.e. the input value of the $j$-th S-box. %For an $X_i$ with $k$ active S-boxes whose index set is $\mathfrak{K}=\{j_0,\cdots,j_{k-1}\}$, we denote it by $X_i[j_0]=x_0,\cdots,X_i[j_{k-1}]=x_{k-1}$ where $x_t\neq 0,\forall 0\leq t<k$ and $X_i[t]=0$ if $t\notin \mathfrak{K}$.

\subsection{Differential Cryptanalysis}

In differential cryptanalysis, the attacker tries to find an exploitable \textit{differential propagation}, which is a difference pair, with high probability to distinguish the target symmetric-key primitive from a random permutation. 
%That is, considering a couple of $n$-bit $a$ and $a'$ with $\alpha=a\oplus a'$, we let $\beta=h(a)\oplus h(a')$.

\begin{definition}[Differential Probability for $\calP$]
    For a permutation $\calP:\bbF_2^n\rightarrow \bbF_2^n$, the probability of a difference propagation is defined as:
    \begin{align*}
        \bbP(\alpha\xrightarrow{\calP}\beta)=2^{-n}\cdot\Big|\{x\in\bbF_2^n|\calP(x)\oplus\calP(x\oplus\alpha)=\beta\}\Big|.
    \end{align*}
\end{definition}

For a pair chosen uniformly from the set of all pairs $(a,a')$ where $a\oplus a'=\alpha$,
$\bbP(\alpha\xrightarrow{\calP}\beta)$ is the probability that $\calP(a)\oplus \calP(a')=\beta$, ranging from 0 to 1.

Since the fixed-key block cipher $\calE_K$ is a permutation, a differential propagation probability for $\calE_K$ is also defined as above. However, the key $K$ of $\calE_K$ is unknown for the attacker. Thus the \textit{Expected Differential Probability} (EDP) over all keys for $\calE$ is defined as follows:

\begin{definition}[EDP for $\calE$]
    For a block cipher $\calE:\bbF_2^n\rightarrow \bbF_2^k\times\bbF_2^n$, given $\alpha,\beta\in \bbF_2^n$, the EDP of the difference propagation $(\alpha,\beta)$ over a uniformly distributed random key $K\in \bbF_2^k$ is defined as:
    \begin{align*}
        \EDP(\alpha\xrightarrow{\calE}\beta)=2^{-k}\cdot\sum\limits_{K\in \bbF_2^k}\bbP(\alpha\xrightarrow{\calE_K}\beta)
    \end{align*}
\end{definition}

\begin{definition}[Differential Characteristic]
    An $r$-round differential characteristic is a sequence of $r+1$ differences $(\alpha_0,\cdots,\alpha_r)\in(\bbF_2^n)^{r+1}$. Its probability is
    \begin{align*}
        &\bbP(\alpha_0\xrightarrow{\calR_0}\cdots\xrightarrow{\calR_{r-1}}\alpha_r)\\
        =&2^{-n}\cdot\Big|\{x\in\bbF_2^n|\forall i, \calR_i\circ\cdots\circ\calR_0(x)\oplus\calR_i\circ\cdots\circ\calR_0(x\oplus\alpha_0)=\alpha_{i+1}\}\Big|\\
        \approx&\prod\limits_{i=0}^{r-1}\bbP(\alpha_i\xrightarrow{\calR_i^*}\alpha_{i+1})
        =\prod\limits_{i=0}^{r-1}\prod\limits_{j=0}^{m-1}\bbP(\alpha_i[j]\xrightarrow{\calS_i}\beta_i[j])
    \end{align*}
    where $\alpha_{i+1}=\calL(\beta_i),0\leq i<r$. 
\end{definition}

Under the assumption of independent random round keys and the hypothesis of stochastic equivalence \cite{lai1991markov}, the probability of a differential characteristic is calculated round by round and S-box by S-box.

\begin{definition}[Differential]
    An $r$-round differential $(\alpha,\beta)$ is a set of differential characteristics sharing the same input difference $\alpha$ and output difference $\beta$. 
\end{definition}

The probability of a difference propagation is estimated by summing the probabilities of all differential characteristics sharing the same input and output differences, i.e. the probability of the differential:
\begin{align*}
    \bbP(\alpha\xrightarrow{\calP}\beta) \text{ or } \EDP(\alpha\xrightarrow{\calE}\beta)=&\sum\limits_{\substack{\alpha_0=\alpha,\alpha_r=\beta\\\alpha_1,\cdots,\alpha_{r-1}}}\bbP(\alpha_0\xrightarrow{\calR_0}\cdots\xrightarrow{\calR_{r-1}}\alpha_r)\\
    \approx&\sum\limits_{\substack{\alpha_0=\alpha,\alpha_r=\beta\\\alpha_1,\cdots,\alpha_{r-1}}}\prod\limits_{i=0}^{r-1}\prod\limits_{j=0}^{m-1}\bbP(\alpha_i[j]\xrightarrow{\calS_i}\beta_i[j])
\end{align*}

\subsubsection{Truncated Differential \cite{daemen2002design}}
Let $\lambda$ be a linear function corresponding to an $n\times l$ binary matrix $M$. The probability of a \textit{truncated} differential of $\lambda\circ\calP$ is given by:
\[
    \bbP(\alpha\xrightarrow{\lambda\circ\calP}\beta)=\sum\limits_{\omega|\beta=M\omega}\bbP(\alpha\xrightarrow{\calP}\omega).
\]

\subsection{Linear Cryptanalysis}

In linear cryptanalysis, the attacker tries to find an exploitable \textit{linear propagation}, which is a mask pair, revealing an approximate linear relation between the input value and the output value of the target symmetric-key primitive, and thus we can distinguish the target primitive from a random permutation. 

\begin{definition}[Correlation]
    The correlation of a Boolean function $f:\bbF_2^n\rightarrow\bbF_2$ is
    \begin{align*}
        c_f=2^{-n}\cdot\Big(\Big| \{x\in\bbF_2^n|f(x)=0\} \Big|-\Big| \{x\in\bbF_2^n|f(x)=1\} \Big|\Big)
    \end{align*}
\end{definition}

\begin{definition}[Correlation for $\calP$]
    For a permutation $\calP:\bbF_2^n\rightarrow \bbF_2^n$, the correlation of a linear propagation is defined as:
    \begin{align*}
        \Cor(\alpha\xrightarrow{\calP}\beta)=c_{\alpha\cdot x\oplus \beta\cdot\calP(x)}
    \end{align*}
    %$\alpha\cdot x\oplus \beta\cdot\calP(x)$ is a linear approximation of $\calP$ and we denote $c_{\alpha\cdot x\oplus \beta\cdot\calP(x)}$ by $\Cor(\alpha\xrightarrow{\calP}\beta)$.
\end{definition}

The fixed-key block cipher $\calE_K$ is a permutation. However, the key $K$ of $\calE_K$ is unknown for the attacker. Thus the \textit{Expected Linear Potential} (ELP) over all keys for $\calE$ is defined as follows:

\begin{definition}[ELP for $\calE$]
    For a block cipher $\calE:\bbF_2^n\rightarrow \bbF_2^k\times\bbF_2^n$, given $\alpha,\beta\in \bbF_2^n$, the ELP of the linear propagation $(\alpha,\beta)$ over a uniformly distributed random key $K\in \bbF_2^k$ is defined as:
    \begin{align*}
        \ELP(\alpha\xrightarrow{\calE}\beta)=2^{-k}\cdot\sum\limits_{K\in \bbF_2^k}\Cor^2(\alpha\xrightarrow{\calE_K}\beta)
    \end{align*}
\end{definition}

\begin{definition}[Linear Characteristic]
    An $r$-round linear characteristic is a sequence of $r+1$ masks $(\alpha_0,\cdots,\alpha_r)\in(\bbF_2^n)^{r+1}$. Its correlation is calculated by
    \begin{align*}
        \Cor(\alpha_0\xrightarrow{\calR_0}\cdots\xrightarrow{\calR_{r-1}}\alpha_r)
        =(-1)^{\oplus_{i=0}^r \alpha_i\cdot W_i}\cdot\prod\limits_{i=0}^{r-1}\Cor(\alpha_i\xrightarrow{\calR_i^*}\alpha_{i+1})
    \end{align*}
\end{definition}

\begin{definition}[Linear Hull]
    An $r$-round linear hull $(\alpha,\beta)$ is a set of linear characteristics sharing the same input mask $\alpha$ and output mask $\beta$. 
\end{definition}

For a permutation, the correlation of a linear propagation is calculated by the signed sum of correlations all linear characteristics sharing the same input and output masks:
\begin{align*}
    \Cor(\alpha\xrightarrow{\calP}\beta)=&\sum\limits_{\alpha_1,\cdots,\alpha_{r-1}}\Cor(\alpha_0\xrightarrow{\calR_0}\cdots\xrightarrow{\calR_{r-1}}\alpha_r)\\
    =&\sum\limits_{\alpha_1,\cdots,\alpha_{r-1}}\prod\limits_{i=0}^{r-1} (-1)^{\oplus_{i=0}^r \alpha_i\cdot W_i} \prod\limits_{j=0}^{m-1}\Cor(\alpha_i[j]\xrightarrow{\calS_i}\beta_i[j]).
\end{align*}

For a key-alternating block cipher, the ELP of a linear propagation is calculated by summing the correlation squares of all linear characteristics sharing the same input and output masks according to Theorem 7.9.1 in \cite{daemen2002design}:
\begin{align*}
    \ELP(\alpha\xrightarrow{\calE}\beta)=&\sum\limits_{\alpha_1,\cdots,\alpha_{r-1}}\Cor^2(\alpha_0\xrightarrow{\calR_0}\cdots\xrightarrow{\calR_{r-1}}\alpha_r)\\
    =&\sum\limits_{\alpha_1,\cdots,\alpha_{r-1}}\Cor^2(\alpha_0\xrightarrow{\calR_0^*}\cdots\xrightarrow{\calR_{r-1}^*}\alpha_r)\\
    =&\sum\limits_{\alpha_1,\cdots,\alpha_{r-1}}\prod\limits_{i=0}^{r-1}\prod\limits_{j=0}^{m-1}\Cor^2(\alpha_i[j]\xrightarrow{\calS_i}\beta_i[j])
\end{align*}
where $\beta_i=\calL^T(\alpha_{i+1}),0\leq i<r$.



\subsection{Concepts in Graph Theory} \label{sec:graph-concept}

A \textit{directed graph} $G(V, E)$ consists of a nonempty and finite set of \textit{vertices} $V$ and a set $E$ of ordered pairs of distinct vertices called \textit{edges}. We denote a directed edge from a vertex $u\in V$ to a vertex $v\in V$ by $u\rightarrow v$. $u$ is called the head of the edge and $v$ is called the tail of the edge. Each edge $u\rightarrow v$ can be associated with a \textit{cost} and we denote it by $c(u\rightarrow v)$. A \textit{path} $p_{u,v}$ is a sequence of vertices $(u=v_0,v_1,\cdots,v_{k-1},v=v_k)$ such that $v_i\rightarrow v_{i+1}\in E, 0\leq i<k$. The \textit{length} of the path is
\[
    l(p_{u,v})=k,
\]
the \textit{cost} of the path is
\[
    c(p_{u,v})=\prod\limits_{i=1}^{k}c(v_{i-1}\rightarrow v_i).
\]
A \textit{hull} of $(u,v)$ is defined as the set of all paths $p_{u,v}$ leading from $u$ to $v$. More specifically, we define a $k$-length hull of $(u,v)$, denoted by $h^k_{u,v}$, as the set of all paths $p_{u,v}$ satisfying $l(p_{u,v})=k$. The cost of $h^k_{u,v}$ is
\[
    c(h^k_{u,v})=\sum\limits_{l(p_{u,v})=k} c(p_{u,v}).
\]

A path $p_{u,u}$ whose head is equal to its tail is called a \textit{circuit}. A circuit is \textit{elementary} if no vertex but the first and last appears twice. Two circuits are distinct if one is not a cyclic permutation of the other. An induced subgraph $G'=(V',E')$ is a (maximal) \textit{strong component} of $G$ if for all $u, v\in V'$ there exist paths $p_{uv}$ and $p_{vu}$ and this property holds for no subgraph of $G$ induced by a vertex set $\overline{V'}$ such that $V' \subset \overline{V'} \subseteq V$. A vertex in a strong component must belong to a circuit. And a vertex in a circuit must belong to a strong component. 

Let $G$ be a directed graph with vertices $V$ and edges $E$. If the vertices in $V$ are partitioned into $l$ subsets $S_0,\cdots,S_{l-1}$, called \textit{stages}, such that any edge in $E$ has the form $u\rightarrow v$ with $u\in S_i$ and $v\in S_{i+1}$, $0\leq i<l$. We call the graph a \textit{multistage graph}.

\subsubsection{Associating Characteristics with a Directed Graph}

For a directed graph $G$ with $V$ as its vertex set and $E$ as its edge set, we associate every vertex to a difference or mask. An edge $u\rightarrow v$ exists if the corresponding 1-round characteristic is valid. The cost of the edge can be associated with the differential probability, correlation or correlation square of the 1-round characteristic. A path with length $k$ is a $k$-round characteristic. A circuit is an iterative characteristic. A $k$-length hull is a $k$-round differential or linear hull. 

%\subsubsection{Notation} In this paper, we will not distinguish a vertex from a difference or mask value, an edge from a 1-round trail, a path from a trail, a weight from a differential probability or linear correlation. Note that the term "weight" has several meanings in other literatures, like the hamming weight of a difference or mask value, the negative logarithm of a differential probability or linear correlation. 

